---
title: "Confidence Interval"
author: "Tanyya Varshney"
output: html_document
---

##Problem Statement
Estimate the 99% confidence interval for the mean body fat percentage in the population.

### Loading packages and data set
```{r message=FALSE, warning=FALSE}
#loading packages
library(car)
library(mosaic)
library(Hmisc)

#loading data set 
Body_data <- read.csv("Body.csv",header = TRUE,sep = ",")

#Cleaning the data
Body_data$Sex <- factor(Body_data$Sex, levels = c(0,1),labels = c("Female","Male"))
```

###Assumptions
1. Unknown Population standard deviation
In real world scenario, we don't know the population standard deviation. Here also, we know the sample standard deviation but the entire population paramters are unknown to us. 
Thus, we need estimate the population standard deviation from the sample standard deviation.
For this purpose we use the <b> t distribution </b> for calculating the confidence interval.

2. Normality of the data
As seen from task 1, our sample size is 252 (large sample as it is >30)and by Central limit Theorm we can say that the data is <b>Normally disributed</b>.
Also, the normality of the data can be checked using the Q-Q plot.

```{r}
qqPlot(Body_data$BFP_Brozek, dist="norm")

```
As seen from the Q-Q plot 95% of the data lies between the dotted lines, thus we can assume that our data is normally distributed.
```{r}
#Confidence interval using t-test
confint(t.test( ~ BFP_Brozek, data = Body_data,conf.level = 0.99))
```
The 99% Confidence Interval for body fat percentage is [17.67 20.21]